A Comparison of Graph Processing Systems

### 2020-09-18 documentation/paper/main.tex
kleine änderungen
weitere kleine Änderungen
Appendices merged

\section{Discussion}
\todo{Section}

@@

\appendices
\todo{Beide zusammenfassen}
\section{Installation Guides}\label{app:installationGuides}
The complete installation guides with steps on how to run the same algorithms we used is available in our repository\footnote{\url{https://github.com/SerenGTI/Forschungsprojekt/tree/master/documentation}}

In case of frameworks like Giraph, where for example no BFS algorithm is provided by the framework itself, the algorithm and a guide on how to include it in the framework can be found in the repository as well.

\section{Conversion Tool}\label{app:conversionTool}
In order to

We have written a number of conversion tools and installation guides to help
users or developers with the use of the tested frameworks.

Our GitHub repository: \url{http://www.github.com/serengti/Forschungsprojekt}.

>>>>

\section{Discussion}
\todo{Hier zunächst mal ein kurzer Vergleich zwischen Distributed und Single Node wo sinnvoll, dann zwischen den Frameworks und so weiter..}

@@

\appendix
\label{app:installationGuides}\label{app:conversionTool}
We provide a set of installation guides, describing setup and usage of each of the presented frameworks. In case of Giraph, where for example no BFS algorithm is provided by the framework itself, the algorithm and a guide on how to include it in the framework is provided as well. Furthermore, the conversion tool we described to convert between the different graph input formats is available alongside the guides in our repository\footnote{\url{https://github.com/SerenGTI/Forschungsprojekt/tree/master/documentation}}.
